---
title: "Work from Home"
author: "M. Chae"
date: '2020 4 4 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Survey result about work from home  

This document summarize the survey result of work from home for three weeks because of the COVID-19.


### Description of the survey 

* Background: The number of confirmed cases of COVID-19 is increasing, so we decided to take a work from home policy. 
* Purpose: examination of the effect of work from home 
* Survey period: March 2020 
* Sample: n = 436


## The level of cooperation & efficiency by position/responsibility

```{r include=FALSE}
library(tidyverse)
library(readr)
library(car)
read.csv.any <- function(text, sep = "", ...) {
  encoding <- as.character(guess_encoding(text)[1,1])
  setting <- as.character(tools::file_ext(text))
  if(sep != "" | !(setting  %in% c("csv", "txt")) ) setting <- "custom"
  separate <- list(csv = ",", txt = "\n", custom = sep)
  result <- read.table(text, sep = separate[[setting]], fileEncoding = encoding, ...)
  return(result)
}
df <- read.csv.any("c:/Users/MC/R/work-from-home-survey/survey_num.csv", header = TRUE, na.strings = c("NA", ""))
df$efficiency <- recode(df$efficiency, "'100' = 3 ; '100~80' =  2 ; '150~100' = 4")
df$efficiency <- as.numeric(df$efficiency)
df_stfc <- df %>% 
  group_by(position, responsibility) %>% 
  summarise(mean_stfc = mean(satisfaction, na.rm = TRUE))
df_stfc

df_prvc <- df %>% 
  group_by(position, responsibility) %>% 
  summarise(mean_prvc = mean(privacy, na.rm = TRUE))
df_prvc

df_effi <- df %>% 
  group_by(position, responsibility) %>% 
  summarise(mean_effi = mean(efficiency, na.rm = TRUE))
df_effi

df_effi_days <- df %>% 
  group_by(days, position, responsibility) %>% 
  summarise(mean_effi = mean(efficiency, na.rm = TRUE))
df_effi_days

df_coop <- df %>% 
  group_by(position, responsibility) %>% 
  summarise(mean_coop = mean(cooperation))
df_coop

df_coop_days <- df %>% 
  group_by(days, position, responsibility) %>% 
  summarise(mean_coop = mean(cooperation))
df_coop_days
```


```{r warning=FALSE}
ggplot(df_coop, aes(position, mean_coop, fill = responsibility))+
  geom_col(position = "dodge")

ggplot(df_coop_days, aes(days, mean_coop, fill = position))+
  geom_col(position = "dodge")

ggplot(df_effi, aes(position, mean_effi, fill = responsibility))+
  geom_col(position = "dodge")

ggplot(df_effi_days, aes(days, mean_effi, fill = position))+
  geom_col(position = "dodge")
```

## The relation between efficiency and cooperation

```{r warning=FALSE}
ggplot(df, aes(efficiency, cooperation))+
  geom_point(mapping = aes(color = days, shpae = days))+
  geom_smooth(color = 'black', fill = 'grey')+
  facet_wrap(~position)
```

## The level of efficiency & cooperation by the duration 


```{r warning=FALSE}
ggplot(df_coop_days, aes(days, mean_coop))+
  geom_point(mapping = aes(color = position, shape = responsibility))+
  geom_boxplot()+
  theme_bw()

ggplot(df_effi_days, aes(days, mean_effi))+
  geom_point(mapping = aes(color = position, shape = responsibility))+
  geom_boxplot()+
  theme_bw()
```

## Correlations between the four variables

```{r message=FALSE, warning=FALSE}
df_narm <- na.omit(df)
cor(df[,c(3:6)],method=c("pearson"))

library(PerformanceAnalytics)
chart.Correlation(df_narm[,c(3:6)],pch=19)

```

## Comments from repondents

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(KoNLP) #loading the required libraries for wordcloud 
library(wordcloud)
library(stringr)
library(XML)
library(rvest)
library(tm)
library(igraph)
library(wordcloud2)
library(arules)
library(combinat)
library(multilinguer)

.libPaths()
useSejongDic()

comments <- readLines("c:/users/MC/R/work-from-home-survey/comments.txt", encoding = "UTF-8")

comments <- paste0(comments, collapse = "")

nouns <- extractNoun(comments)
nouns1 <- unlist(nouns)
nouns2 <- Filter(function(x) {nchar(x) <= 20 & nchar(x) > 1}, nouns1)

nouns2 <- gsub(" ","", nouns2)
nouns2 <- gsub("<.+?>|\t", "", nouns2)
nouns2 <- gsub("\\d+","" ,nouns2)	
nouns2 <- gsub("\\.","" ,nouns2) 
nouns2 <- gsub("재택근무","" ,nouns2)
nouns2 <- gsub("생각","" ,nouns2)
nouns2 <- gsub("업무","" ,nouns2)
nouns2 <- gsub("근무","" ,nouns2)
nouns2 <- gsub("재택","" ,nouns2)
nouns2 <- gsub("하기","" ,nouns2)
nouns2 <- gsub("관련","" ,nouns2)
nouns2 <- gsub("들이","" ,nouns2)
str(nouns2)

nouns3 <- Filter(function(x) {nchar(x) <= 20 & nchar(x) > 1}, nouns2)

wordcount <- table(nouns3)

windowsFonts(malgun=windowsFont("맑은고딕"))
wordcloud2(data=wordcount, minSize = 5, 
           minRotation = 0, maxRotation = 0, rotateRatio = 1, 
           fontFamily='맑은고딕',size=0.8)
```

